Hijacking Malaria Simulators with Probabilistic Programming

### 2019-04-26 paper/icml_ai4good/main.tex
section 3

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
\usepackage{tabularx}
\usepackage{listings}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{todonotes}
\usepackage{tikz-cd}

@@

After a variable has been sampled, it is sent to the PPS using \textit{pyprob\_cpp::sample}, alongside with its simulator source trace. This allows the PPS to construct sample trace probabilities and other summary statistics (cf. Section \ref{sec:casestudy}).

@@

  A4 & Potential children deaths

  within the population are simulated \\
  A5 & Potential children deaths within

   the population are simulated \\

>>>>

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
\usepackage{tabularx}
\usepackage{listings}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{todonotes}
\usepackage{tikz-cd}
\usepackage[binary-units=true]{siunitx}

@@

After a variable has been sampled, it is sent to the PPS using \textit{pyprob\_cpp::sample}, alongside with its simulator source trace. This allows the PPS to construct sample trace probabilities and other summary statistics (cf. Section \ref{sec:casestudy}). 
Finally, the entry point to the simulator, i.e. \textit{main} in C++, is replaced by a special \textit{forward} call, in this case \textit{pyprob\_cpp::forward}.
This allows the PPS to generate roll outs from the simulator remotely.

\paragraph{Population-based simulators} In contrast to the setup used by \cite{Baydin}, who interface a particle physics simulator that creates a single trace per \textit{forward} call, a population-based simulator creates a trace per population member. This means that e.g. in EMOD, a standard scenario simulation rollout over the span of $3$ years  
with a population of size $n=5000$ \cite{smith} will generate about $ \SI{4}{\tera\byte}$ of raw trace data. Unlike with \citep{Baydin}, this amount of data cannot possibly be kept in RAM, which makes \textit{a posteriori} trace analysis very inefficient. 
In order to deal with the shortcomings of \textit{pyprob} in a population-based simulator context, we therefore extend the framework to be able to do trace analysis on the fly.

By extending \textit{pyprob} to handle population-based simulators, the PPS can now track all stochastic random variables that are created within the simulator, which then allows us to generate trace plots and path probabilities associated to the execution paths of the program.
The corresponding increase of simulator transparency helps reinstate much needed trust between policymakers and evidence-based methods.

@@

  A4, A5 & Potential child deaths

  within the population are simulated \\
